They're Clutching up! Team Momentum in Round-Based Esports

### 2022-08-12 paper/paper.qmd
render paper

---
title: "They're Clutching up! Team Momentum in Round-Based Esports"
format:
  arxiv-pdf:
    keep-tex: true  
  arxiv-html: default
author:
  - name: Tony ElHabr
    affiliations:
      - name: Georgia Institute of Technology
    email: anthonyelhabr@gmail.com
    url: https://tonyelhabr.rbind.io
abstract: |
  My research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD).

@@

@@

CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022. The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era. Data was collected in spreadsheets by community member "IOUTurtle".[^5]

[^5]: Data: https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle

@@

CoD is fairly unique compared to other esports in that it runs on an annual lifecycle, where a new game is published every year under the same title. Each new game bears resemblance to past ones, often introducing relatively small variations ("improvements") to graphics, game modes, and other facets of gameplay. The data set denotes which CoD game a given CoD SnD series was played,

@@

Streaks and momentum is one of the most frequently published topics in sports analytics. We often use these interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not. When considering

Despite the plethora of existing research on momentum in sports, its yet to be investigated heavily in esports. [@article-journal]

>>>>

---
title: "They're Clutching up! Team Momentum in Round-Based Esports"
execute: 
  include: false
  echo: false
  eval: false
format:
  arxiv-pdf:
    keep-tex: true  
  arxiv-html: default
author:
  - name: Tony ElHabr
    affiliations:
      - name: Georgia Institute of Technology
    email: anthonyelhabr@gmail.com
    url: https://tonyelhabr.rbind.io
abstract: |
  My research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD).

@@

```{r}
#| label: setup
#| eval: true
library(dplyr)
library(dplyr)
library(qs)
library(scales)

cod_rounds <- qs::qread('../cod_rounds.qs')
```

```{r}
#| label: setup-eval
library(tidyverse)
library(extrafont)
library(ggtext)
library(ggsci)
library(ggnewscale)
library(magick)
library(broom)
library(knitr)

background_color <- '#000000' ## to match slide background
text_color <- '#191919'

font <- 'Titillium Web'
extrafont::loadfonts(quiet = TRUE)
theme_set(theme_minimal())
theme_update(
  text = element_text(family = font),
  title = element_text(size = 14, color = text_color),
  plot.title = element_text(face = 'bold', size = 20, color = text_color),
  plot.title.position = 'plot',
  plot.subtitle = element_text(size = 14, color = '#f1f1f1'),
  axis.text = element_text(color = 'white', size = 14),
  axis.title = element_text(size = 14, color = text_color, face = 'bold', hjust = 0.99),
  axis.line = element_blank(),
  panel.grid.major = element_line(color = text_color),
  panel.grid.minor = element_line(color = text_color),
  panel.grid.minor.x = element_blank(),
  panel.grid.minor.y = element_blank(),
  strip.text = element_text(color = text_color, size = 16, face = 'bold'),
  plot.margin = margin(10, 10, 10, 10),
  plot.background = element_rect(fill = background_color, color = background_color),
  plot.caption = element_text(size = 12, color = text_color, hjust = 1),
  plot.caption.position = 'plot',
  plot.tag = ggtext::element_markdown(size = 12, color = text_color, hjust = 0),
  plot.tag.position = c(0.01, 0.01),
  panel.background = element_rect(fill = background, color = background_color)
)
update_geom_defaults('text', list(family = font, size = 10 / .pt, fontface = 'bold'))
update_geom_defaults('point', list(color = text_color))
update_geom_defaults('segment', list(color = text_color))
```

```{r}
#| label: descriptive-cod-snd-stats
#| eval: true
cod_n_series <- cod_rounds |> 
  distinct(series_id, team) |> 
  nrow()

cod_n_rounds <- cod_rounds |> 
  distinct(series_id, team, round) |> 
  nrow()
cod_n_rounds / cod_n_series
## mean(cod_rounds$n_rounds) ## should this be the same?

cod_o_win_prop_const <- cod_rounds |> 
  filter(is_offense) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop)
```

```{r}
#| label: cod-funcs
common_cod_labs <- function(...) {
  list(
    ...,
    labs(
      caption = 'CDL SnD major and qualifier series, 2020 - 2022'
    )
  )
}

common_cod_heatmap_layers <- function(...) {
  list(
    ...,
    guides(
      fill = 'none'
    ),
    scale_x_continuous(
      labels = 0:5,
      breaks = seq(0.5, 5.5, by = 1),
      expand = c(0, 0)
    ),
    scale_y_continuous(
      labels = 0:5,
      breaks = seq(0.5, 5.5, by = 1),
      expand = c(0, 0),
      sec.axis = sec_axis(
        trans = I, 
        name = ' ', 
        breaks = seq(0.5, 5.5, by = 1), 
        labels = rep('', 6)
      )
    ),
    theme(
      panel.grid.major = element_blank(),
      axis.title = element_text(hjust = 0.5),
      plot.title = ggtext::element_markdown(hjust = 0.5),
      axis.text = element_text(size = 16, face = 'bold')
    ),
    common_cod_labs(),
    labs(
      x = "Offensive Team's # of Pre-Round Wins",
      y = "Defensive Team's # of Pre-Round Wins"
    )
  )
}

.dpi <- 300
save_plot_for_paper <- function(
    p, 
    filename = paste0(str_remove(deparse(substitute(p)), '^p_'), '.png'), 
    width = 7.5, 
    height = width / 1.5,
    units = 'px',
    dpi = .dpi,
    ...
) {

  path <- ggsave(
    plot = p,
    filename = file.path('plots', filename),
    width = width * dpi,
    height = height * dpi,
    units = units,
    dpi = dpi,
    ...
  )
  is_cod <- filename |> str_detect('cod_')
}

heatmap_tile <- function(..., .fill) {
  list(
    ...,
    geom_rect(
      color = background_color,
      aes(
        fill = .data[[.fill]],
        xmin = pre_cumu_w, 
        ymin = pre_cumu_l,
        xmax = pre_cumu_w + 1,
        ymax = pre_cumu_l + 1
      )
    )
  )
}

heatmap_text_layer <- function(..., .op, .df, .label, .num, .color, .threshold, .labeller, .size = 11 / .pt) {
  .df_filt <- .df |> filter(`.op`(.df[[.label]], .threshold))
  if(nrow(.df_filt) == 0) {
    return(list(...))
  }
  list(
    ...,
    geom_text(
      data = .df_filt,
      color = .color,
      size = .size,
      fontface = 'bold',
      aes(
        label = .labeller(.df = .df_filt, .label = .label, .num = .num),
        x = .data$pre_cumu_w + 0.5, 
        y = .data$pre_cumu_l + 0.5
      )
    )
  )
}

heatmap_text_layers <- function(
    ..., 
    .df,
    .threshold,
    .labeller,
    .f
) {
  list(
    ...,
    .f(.df = .df, .threshold = .threshold, .labeller = .labeller, .emphasize = 'low'),
    .f(.df = .df, .threshold = .threshold, .labeller = .labeller, .emphasize = 'high')
  )
}

cod_heatmap_seq_labeller <- function(.df, .label, .num) {
  sprintf(
    '%s\n(%s)',
    scales::percent(.df[[.label]], accuracy = 1), 
    scales::comma(.df$n)
  )
}

cod_heatmap_seq_labeller <- function(.df, .label, .num) {
  sprintf(
    '%s\n(%s)',
    scales::percent(.df[[.label]], accuracy = 1), 
    scales::comma(.df$n)
  )
}

o_round_win_text_layer <- function(
    ..., 
    .df,
    .threshold,
    .labeller,
    .label = 'win_round_prop',
    .num = 'win_round',
    .emphasize
) {
  if(.emphasize == 'low') {
    op <- `<`
    .color <- background_color
  } else {
    op <- `>=`
    .color <- 'white'
  }
  list(
    ...,
    heatmap_text_layer(
      .df = .df,
      .op = op,
      .label = .label,
      .num = .num,
      .color = .color,
      .threshold = .threshold,
      .labeller = .labeller,
      .size = 11 / .pt
    )
  )
}

cod_heatmap_div_labeller <- function(.df, .label, .num) {
  sprintf(
    '%+.1f\n(%s)', 
    100 * .df[[.label]], 
    scales::comma(.df$n)
  )
}

o_round_win_over_expected_text_layer <- function(
    ..., 
    .df, 
    .threshold,
    .labeller,
    .emphasize
) {
  if(.emphasize == 'low') {
    op <- `<`
    .color <- 'white'
  } else {
    op <- `>=`
    .color <- background_color
  }
  list(
    ...,
    heatmap_text_layer(
      .df = .df,
      .op = op,
      .label = 'diff_win_round_prop',
      .num = 1,
      .color = .color,
      .threshold = .threshold,
      .labeller = .labeller
    )
  )
}

extract_ggsci_mid_color <- function(palette) {
  ggsci::pal_material(palette, n = 3)(2)[2]
}

ggsci_purple <- extract_ggsci_mid_color('purple')
ggsci_green <- extract_ggsci_mid_color('green')
ggsci_cyan <- extract_ggsci_mid_color('cyan')
ggsci_brown <- extract_ggsci_mid_color('brown')
```

```{r}
#| label: cod_rounds-calcs
cod_round_and_series_win_prop_by_side <- cod_rounds |> 
  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
  summarize(
    n = n(),
    across(c(win_round, win_series), sum)
  ) |> 
  ungroup() |> 
  mutate(
    win_round_prop = win_round / n,
    win_series_prop = win_series / n
  )

cod_e_o_win_series_prop <- crossing(
  pre_cumu_w = 0:5,
  pre_cumu_l = 0:5
) |> 
  mutate(
    n_remain_max = 11 - (pre_cumu_w + pre_cumu_l),
    n_remain_w = 6 - pre_cumu_w,
    ## can i account for offense in this by rotating?
    e_win_series_prop = map2_dbl(n_remain_w, n_remain_max, ~sum(dbinom(..1:..2, ..2, 0.5)))
  )
```

@@

CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.[^5] The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era. Data was collected in spreadsheets by community member "IOUTurtle".[^6]

[^5]: CoD is fairly unique compared to other esports in that it runs on an annual lifecycle (released coming in the late fall), where a new game is published every year under the same title. Each new game bears resemblance to past ones, often introducing relatively small variations ("improvements") to graphics, game modes, and other facets of gameplay. During the CDL era, the games released have been Modern Warfare (2020), Cold War (2021) and Vanguard (2022).

[^6]: Data: https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle

@@

@@

There have been only a handful of studies of the distribution of games played in a series, most of which assume a constant probability $p$ of a given team winning a game in the series, regardless of the series state. Observing that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with $p=0.5$, [@mosteller1952] proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $p \approx 0.65$ in each case: (1) a "method of moments", an approach that solves for $p$ from the empirical average number of games won by the loser of the series; (2) maximum likelihood, and (3) maximum chi-square approach. [@chance2020] re-examines the constant probability notion in Major League Baseball's World Series (1923--2018), the National Basketball Association's Finals (1951--2018), and the National Hockey League's Stanley Cup (1939--2018). Chance applies Mosteller's method 1 and 2 and finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series. Chance outlines a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.

Momentum is one of the most frequently published topics in sports analytics. We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not. (sentence about negative recency, hinting at "hot hand"... [@miller2018] debunking findings from [@gilovich1985])

Despite the plethora of existing research on games played and momentum in sports, these topics have yet to be investigated heavily in esports. Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike ([@xenopoulos2022]) and Valorant ([@derover2021]), both of which are round-based like CoD SnD. However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^7]\[\^8\]

[^7]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).

# 3. Methodology

# 4. Results and discussion

### 2022-08-12 paper/paper.tex
render paper

\title{They're Clutching up! Team Momentum in Round-Based Esports}
\author{
Tony ElHabr\\\\Georgia Institute of
Technology\\\\\href{mailto:anthonyelhabr@gmail.com}{anthonyelhabr@gmail.com}}
\date{}
\begin{document}
\maketitle
\begin{abstract}
My research investigates patterns in round win percentages in
professional matches (series) of two popular first-person shooter games,
Call of Duty (Search and Destroy mode) and Valorant.

First, I find evidence in Call of Duty (COD) defying the naive
hypothesis that a series represents a sequence of independent events
(rounds), with each team having a constant 50\% probability of winning a
given round.

Second, I examine post-streak round win probability. For COD, in which
teams play first to 6 round wins (maximum 11 rounds), I find that teams
perform significantly worse than expected after streaks of 2, 3, and 4
wins when series end up going to 9, 10, or 11 rounds, even after
accounting for the ``hot-hand'' phenomenon. In Valorant, which requires
one side to win 13 rounds for the series victory, there is evidence of
performing better than expected after streaks of up to 8 wins, which is
perhaps not shocking given the economy aspect of the game.

Third, I compare win percentages in round one versus all other rounds,
hypothesizing that there may be some advantage on either side when there
is no prior information about how the opponent intends to play a given
map in either game. I find one COD map for which there seems to be a
significant defensive advantage in round one, but none otherwise.

Finally, I evaluate behavior when teams have two rounds left to win the
series, observing a peak in COD offensive win percentages in the 4-4
state, and no such oddity in Valorant.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, enhanced, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden]}{\end{tcolorbox}}\fi

Sit nunc at convallis fringilla semper! Penatibus vivamus eget malesuada
cursus fames magnis potenti. Venenatis ligula enim conubia laoreet orci
class ligula? Massa sem sed enim risus ut mattis inceptos nisl elementum
mattis. Nostra ultricies habitant donec vitae luctus proin gravida
placerat ac libero imperdiet. Auctor habitasse faucibus ultricies purus
eget sociis ultrices habitasse nec ad aptent lectus rutrum proin potenti
montes sodales posuere convallis tempor erat egestas magna lectus sociis
mollis purus.

Dolor turpis euismod himenaeos interdum felis dictum tempus euismod
tortor aliquam? Eget interdum vehicula laoreet quam. Mollis justo cursus
ad blandit feugiat pulvinar sem sodales bibendum. Leo leo magna pulvinar
metus lacinia nam fringilla maecenas duis dis suscipit aenean natoque
sem metus quam risus sagittis convallis primis sociis id dictumst.

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Amet ultricies dignissim varius potenti suscipit justo phasellus dui
ullamcorper luctus suscipit vulputate. Sagittis enim volutpat ultrices
diam curabitur potenti platea euismod vel libero primis feugiat. Nibh
potenti habitant ultricies dictum sociis class at vehicula eu
vestibulum. Curabitur iaculis.

Consectetur est eleifend turpis morbi magna porttitor bibendum ut
blandit aliquet lacus. Nostra iaculis torquent parturient id fermentum
montes at himenaeos. Magna congue blandit fames egestas at inceptos? Id
maecenas blandit maecenas accumsan ridiculus mollis nullam justo
pulvinar elementum inceptos habitant risus.

\newpage{}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

>>>>

\title{They're Clutching up! Team Momentum in Round-Based Esports}
\author{
Tony ElHabr\\\\Georgia Institute of
Technology\\\\\href{mailto:anthonyelhabr@gmail.com}{anthonyelhabr@gmail.com}}
\date{}
\begin{document}
\maketitle
\begin{abstract}
My research investigates patterns in round win percentages in
professional Search and Destroy (SnD) matches of the popular
first-person shooter game Call of Duty (CoD).

First, I find evidence in CoD defying the naive hypothesis that a series
represents a sequence of independent events (rounds), with each team
having a constant 50\% probability of winning a given round.

Second, I examine post-streak round win probability. I find that teams
perform significantly worse than expected after streaks of 2, 3, and 4
wins when series end up going to 9, 10, or 11 (maximum) rounds, even
after accounting for the ``hot-hand'' phenomenon.

Third, I compare win percentages in round one versus all other rounds,
hypothesizing that there may be some advantage on either side when there
is no prior information about how the opponent intends to play a given
map in either game. I find only one instance for which there seems to be
a significant defensive advantage in round one.

Finally, I evaluate behavior when teams have two rounds left to win the
series, observing a peak in COD offensive win percentages in the 4-4
state, and no such oddity in Valorant.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{1. Introduction}\label{introduction}}

\hypertarget{description-of-call-of-duty-search-and-destroy}{%
\subsection{1.1 Description of Call of Duty Search and
Destroy}\label{description-of-call-of-duty-search-and-destroy}}

Call of Duty (CoD), first released in 2003, is one of the most popular
first-person shooter (FPS) video game franchises of all-time. Tthe most
popular mode in the competitive scene is ``Search and Destroy'' (SnD),
which bears resemblance to ``Bomb Defusal'' in Counter-Strike and
``Plant/Defuse'' in Valorant, two other FPS games played in professional
leagues. SnD is one-sided game mode in which one team, the offensive
side, tries to destroy one of two designated bomb sites on the
map.\footnote{as}

In professional CoD, a team must win six rounds of SnD to win the
match.\footnote{A maximum of 11 even rounds can be played. There is no
  ``sudden death'' or ``win by two'' rule like there are for SnD
  equivalent in professional Counter-Strike and Valorant matches.} A
round can end in one of four ways:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  One team eliminates all members of the other team prior to a bomb
  plant. (Eliminating team wins.)
\item
  The offensive team eliminates all members of the defensive team after
  a bomb plant.\footnote{\begin{itemize}
    \tightlist
    \item
      The bomb can be picked up by any member of the offensive team.
    \item
      The bomb carrier is not obstructed at all by carrying the bomb
      (i.e.~movement is the same, weapon usage is the same).
    \item
      The defense does not get any visual indication for who is carrying
      the bomb.
    \item
      A bomb plant takes five seconds. The timer resets if the player
      stops planting site prior to completing it.
    \item
      A bomb defuse takes seven seconds. The timer resets if the player
      ``drops'' the bomb.
    \item
      The bomb takes 45 seconds to defuse after being planted.
    \end{itemize}} (Offense wins.)
\item
  The defensive team defuses the bomb after a bomb plant.\footnote{Often
    the defensive team will try to eliminate all team members prior to
    making the defuse, but in some cases, they may try to ``ninja''
    defuse.} (Defense wins.)
\item
  The offensive team does not make a plant by the time the round timer
  ends. (Defense wins.)
\end{enumerate}

Teams take turns playing offense and defense every round.

\hypertarget{data}{%
\subsection{1.2 Data}\label{data}}

CoD has roughly gone through three eras of professional gaming: (1)
Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World
League (CWL), initiated in 2016; and (3) the 12-franchise CoD League
(CDL), running since 2020 and completing three year-long ``seasons''
completed as of August 2022.\footnote{CoD is fairly unique compared to
  other esports in that it runs on an annual lifecycle (released coming
  in the late fall), where a new game is published every year under the
  same title. Each new game bears resemblance to past ones, often
  introducing relatively small variations (``improvements'') to
  graphics, game modes, and other facets of gameplay. During the CDL
  era, the games released have been Modern Warfare (2020), Cold War
  (2021) and Vanguard (2022).} The data set consists of all SnD matches
played in tournaments and qualifiers during the CDL era. Data was
collected in spreadsheets by community member ``IOUTurtle''.\footnote{Data:
  https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle}

I adopt the terminology ``series'' to refer to what CoD SnD players
typically call a ``match'', so as to emulate the terminology of playoff
series in professional leagues like the National Basketball Association,
National Hockey League, and Major League Baseball. A ``game'' or a
``match'' in such leagues is analogous to a ``round'' of CoD SnD.

\hypertarget{my-contribution}{%
\subsection{1.3 My contribution}\label{my-contribution}}

\hypertarget{literature-review}{%
\section{2 Literature review}\label{literature-review}}

There have been only a handful of studies of the distribution of games
played in a series, most of which assume a constant probability \(p\) of
a given team winning a game in the series, regardless of the series
state. Observing that the American League had dominated the National
League in Major League Baseball's (MLB) World Series matchups, implying
that matchups should not modeled with \(p=0.5\), (Mosteller 1952)
proposed three approaches for identifying the optimal constant
probability value of the stronger team in the World Series, finding
\(p \approx 0.65\) in each case: (1) a ``method of moments'', an
approach that solves for \(p\) from the empirical average number of
games won by the loser of the series; (2) maximum likelihood, and (3)
maximum chi-square approach. (Chance 2020) re-examines the constant
probability notion in Major League Baseball's World Series (1923--2018),
the National Basketball Association's Finals (1951--2018), and the
National Hockey League's Stanley Cup (1939--2018). Chance applies
Mosteller's method 1 and 2 and finds strong evidence against the null
hypothesis of \(p = 0.5\) in the MLB and NHL championship series. Chance
outlines a conditional probability framework (likelihood of winning a
game given the series state) which can exactly explain the distribution
of the number of games played.

Momentum is one of the most frequently published topics in sports
analytics. We often use use ``streaks'' and momentum interchangeably,
but as (Steeger, Dulin, and Gonzalez 2021) note, momentum implies
dependence between events, whereas streaking does not. (sentence about
negative recency, hinting at ``hot hand''\ldots{} (Miller and Sanjurjo
2018) debunking findings from (Gilovich, Vallone, and Tversky 1985))

Despite the plethora of existing research on games played and momentum
in sports, these topics have yet to be investigated heavily in esports.
Work has been done to examine in-round win probability in other FPS
titles such as Counter-Strike ((Xenopoulos, Freeman, and Silva 2022))
and Valorant ((DeRover 2021)), both of which are round-based like CoD
SnD. However, research on round-level trends is spare, perhaps because

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-chance2020}{}}%
Chance, Don. 2020. {``Conditional Probability and the Length of a
Championship Series in Baseball, Basketball, and Hockey.''}
\emph{Journal of Sports Analytics} 6 (2): 111--27.
\url{https://doi.org/10.3233/JSA-200422}.

\leavevmode\vadjust pre{\hypertarget{ref-derover2021}{}}%
DeRover, DeMars. 2021. {``Round Win Probabilities Based on Who's Alive +
Time.''}
\url{https://www.reddit.com/r/VALORANT/comments/n3lpoo/round_win_probabilities_based_on_whos_alive_time/}.

\leavevmode\vadjust pre{\hypertarget{ref-gilovich1985}{}}%
Gilovich, Thomas, Robert Vallone, and Amos Tversky. 1985. {``The Hot
Hand in Basketball: On the Misperception of Random Sequences.''}
\emph{Cognitive Psychology} 17 (3): 295314.

\leavevmode\vadjust pre{\hypertarget{ref-miller2018}{}}%
Miller, Joshua B., and Adam Sanjurjo. 2018. {``Surprised by the Hot Hand
Fallacy? A Truth in the Law of Small Numbers.''} \emph{Econometrica} 86
(6): 20192047.

\leavevmode\vadjust pre{\hypertarget{ref-mosteller1952}{}}%
Mosteller, Frederick. 1952. {``The World Series Competition.''}
\emph{Journal of the American Statistical Association} 47 (259): 355380.

\leavevmode\vadjust pre{\hypertarget{ref-steeger2021}{}}%
Steeger, Gregory M., Johnathon L. Dulin, and Gerardo O. Gonzalez. 2021.
{``Winning and Losing Streaks in the National Hockey League: Are Teams
Experiencing Momentum or Are Games a Sequence of Random Events?''}
\emph{Journal of Quantitative Analysis in Sports} 17 (3): 155170.

\leavevmode\vadjust pre{\hypertarget{ref-xenopoulos2022}{}}%
Xenopoulos, Peter, William Robert Freeman, and Claudio Silva. 2022.
{``Analyzing the Differences Between Professional and Amateur Esports
Through Win Probability.''} In, 34183427.

\end{CSLReferences}
